\thetitle

### 2020-07-21 writing/mutate.tex
tex typo

  \textttt{acquire} & Board game simulation (M. Felleisen)  \\%[1em]

@@

Of course, the gradual typing benchmarks have no mistakes for the rational
programmer to debug. Therefore, we follow
~\cite{lksfd-popl-2020} and we inject bugs with mutation analysis. 
A mutations is a local syntactic change of the code of a program that may
produce a bug. Usually, the outcome of mutating a program
once, dubbed a mutant, can be distinguished from the original program with a test case. 
The better the test suite of a program, the more mutants it can ``kill.''
Thus a big part of research on mutation analysis goes into designing
operations that perform mutations, dubbed mutators, that create mutants 
that are hard to ``kill.'' Unlike the standard mutators, that also ~\cite{lksfd-popl-2020}
use, the mutators we need to evaluate the rational programmer have to be
fined-tune to generate shallow errors. Typed Racket's type system detects 
typos not convoluted logical issues and mutators suitable for our purposes
should target the former rather than the latter.

>>>>

  \texttt{acquire} & Board game simulation (M. Felleisen)  \\%[1em]

@@

Of course, the gradual typing benchmarks have no mistakes for the rational
programmer to debug. Therefore, we follow
~\citet{lksfd-popl-2020} and we inject bugs with mutation analysis. 
A mutations is a local syntactic change of the code of a program that may
produce a bug. Usually, the outcome of mutating a program
once, dubbed a mutant, can be distinguished from the original program with a test case. 
The better the test suite of a program, the more mutants it can ``kill.''
Thus a big part of research on mutation analysis goes into designing
operations that perform mutations, dubbed mutators, that create mutants 
that are hard to ``kill.'' Unlike the standard mutators, which \citet{lksfd-popl-2020}
use, too, the mutators we need to evaluate the rational programmer have to be
fine-tuned to generate shallow errors. Typed Racket's type system detects 
typos not logical mistakes, and mutators suitable for our purposes
should target the former rather than the latter.
